\section{Verification Logic Architecture}

Verification contains the following steps:
\begin{enumerate}
    \item Get input: proof $\pi$ and new state $S$.
    \item Verify placeholder proof $\pi$ (see placeholder verification below).
    \item Update the last confirmed Solana state with $S$
        (see \ref{section:architecture:stateseq}).
\end{enumerate}


\textbf{Placeholder verificaton} part contains the following components:
\begin{enumerate}
    \item \textbf{Proof Deserialization:} Handles the input data processing (marshalling/demarshalling) mechanisms.

    These mechanisms are defined within the \texttt{*\_marshalling}-postfixed files.
    \begin{itemize}
        \item \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/basic_marshalling.sol}
        \item \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/basic_marshalling_calldata.sol}
    \end{itemize}

    \item \textbf{Parameters Initialization} Processes commitment scheme (FRI) parameters from the input data \\
            \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/types.sol}
    \item \textbf{Proof Verification:} Includes a verification of the hash-based commitment scheme and the proof itself.

    The verification itself is defined within the directory \texttt{components}, each of which\footnote{
        For instance, \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/placeholder/verifier_non_native_field_add_component.sol}
    } defines a set of gates
    relevant to particular component.
    Verification algorithm contains:
    \begin{itemize}
        \item Transcript (Fiat-Shamir transfomration to non-interactive protocol) \\
            \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/cryptography/transcript.sol}
        \item Permutation argument: \\
            \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/placeholder/permutation_argument.sol}
        \item Gate Argument depends on the circuit definition and is unique for each circuit.
                    \url{https://github.com/NilFoundation/evm-placeholder-verification/blob/master/contracts/components/non_native_field_add_gen.sol} 
        \item Commitment Scheme verification \\
            \url{https://github.com/NilFoundation/evm-placeholder-verification/tree/master/contracts/commitments}
    \end{itemize}
\end{enumerate}

\subsection{State Proof Sequence Maintenance}
\label{section:architecture:stateseq}

To verify the validator set within the state proof submitted is derived from 
original Solana's genesis data, it is supposed to maintain validator's set state
proofs sequence on in-EVM side in a data structure as follows.

Let $B_{n_1}$ be the last state confirmed on Ethereum. Let us say some prover 
wants to confirm a new $B_{n_2}$ state. Denote by $H_{B}$ the hash of a state $B$.
So a Merkle Tree $T_{n_1, n_2}$ from the set $\{H_{B_{n_1}}, ..., H_{B_{n_2}}\}$


The state proof sequence correctness statement contains (but not bounded by) the following points:
\begin{algorithm}[h!]
    \caption{Proving Statement}
    \label{circuit}
    \begin{enumerate}
        \item Show that the validator set is correct.
        \item Show that the $B_{n_1}$ corresponds to the last confirmed state on Ethereum.
        \item for $i$ from the interval $[n_1 + 1, n_2 - 1]$:
        \begin{enumerate}
            \item Show that $B_{i}$ contains $H_{B_{i - 1}}$ as a hash of the previous state.
        \end{enumerate}
        \item for $i$ from the interval $[n_2, n_2 + 32]$:
        \begin{enumerate}
            \item Show that $B_{i}$ contains $H_{B_{i - 1}}$ as a hash of the previous state.
            \item Show that there are enough valid signatures from the current validator set for $B_{i}$.
        \end{enumerate}
        \item Build a Merkle Tree $T_{n_1, n_2}$ from the set $\{H_{B_{n_1}}, ..., H_{B_{n_2}}\}$.
    \end{enumerate}
\end{algorithm}

$T_{n_1, n_2}$ allows to provide a successful transaction from $\{B_{n_1}, ..., B_{n_2}\}$ to the Ethereum-based proof verificator later.
