\chapter{State Proof Generator}

This introduces a description for Solana's 'Light-Client' state proof generator.

This part's crucial components are defined by Solana's replication protocol
design and consist of:
\begin{enumerate}
    \item Input data format ('Light-Client' state data structure).
    \item Transaction auxiliary proof.
    \item Proof system used for the proof generation.
    \item Circuit definition used for the proof system.
\end{enumerate}

\section{'Light-Client' State}

Block Information $\bar B_k$ is defined as follows:
\begin{itemize}
    \item $k$ - the number of the block
    \item $B_k = H(B_{k - 1} || \texttt{account\_hash} || \texttt{signature\_count\_buf} || b_k || \texttt{validators\_state})$ - bank hash of the block\footnote{See \url{https://docs.solana.com/proposals/simple-payment-and-state-verification\#block-headers}}
    \item $b_k$ Merkle Block
    \item $B_{k - 1}$ - the previous block's bank hash
    \item \texttt{validators\_state} is not implemented for now. 
\end{itemize}

Proof algorithm input is defined as follows:
\begin{itemize}
    \item $n_1$ - current confirmed block number
    \item $n_2$ - new confirmed block number
    \item $\{\bar B_{n_1}, \dots, \bar B_{n_2}, \dots, \bar B_{n_2 + 32}$\} - block information for blocks from $n_1$ to $n_2 + 32$.
    \item $\sigma_0, \dots, \sigma_N$ - signatures for $B_{n_2 + 32}$
\end{itemize}

Approximate code representation of such a state data structure is as follows:
\lstset{language=C++,
    basicstyle=\ttfamily,
    keywordstyle=\color{blue}\ttfamily,
    stringstyle=\color{red}\ttfamily,
    commentstyle=\color{green}\ttfamily,
    morecomment=[l][\color{magenta}]{\#}
}
\begin{lstlisting}[frame=single]
template<typename Hash>
struct block_data {
    typedef typename Hash::digest_type digest_type;

    std::size_t block_number;
    digest_type bank_hash;
    digest_type merkle_hash;
    digest_type previous_bank_hash;
    //    std::vector<vote_state> votes;
};

template<typename Hash, typename SignatureSchemeType>
struct state_type {
    typedef Hash hash_type;
    typedef SignatureSchemeType signature_scheme_type;
    typedef typename signature_scheme_type::signature_type signature_type;

    std::size_t n_1 confirmed;
    std::size_t n_2 new_confirmed;
    std::vector<block_data<hash_type>> repl_data;
    std::vector<signature_type> signatures;
};
\end{lstlisting}

Validator state-representing data structure (\texttt{vote\_state}) supposes such
a state to begin being handled by Solana replication protocol (or its
implementation) for handling the tracking of votes state being unchanged 'till
the end of epoch.

\section{Transaction Proof}

Since state proof sequence is represented as a short Merkle-tree fingerprint and 
does not allow to check transactions without additional mechanisms (as described
in \ref{subsec:stateseq}), there is a need to introduce additional transaction 
proof as simple Merkle-tree inclusion proofs with low verification costs. 

Recall the current state representation on the Ethereum side. 
$H(T_{n_1, n_2})$ is a Merkle tree root of blocks $\{n_1, ..., n_2\}$.
Each block $n_i$ contains transactions tree $Tx_{n_i}$ with a root $H(Tx_{n_i})$.

The prover wants to show that transaction $tx$ was included in the block $n_i$.
Let $D_{n_1, n_2}$ be a hash table.
\begin{enumerate}
    \item If transaction can be spent only once (i.e. it is not a "state-check" transaction):
        \begin{enumerate}
            \item Check that $D_{n_1, n_2}$ does not contain $H(tx)$. 
        \end{enumerate}
    \item The prover provides path of $tx$ to the $H(Tx_{n_i})$ and shows that $H(Tx_{n_i})$ is included in $n_i$.
    \item The prover provides the path of $H(n_i)$ to the $H(T_{n_1, n_2})$.
    \item If transaction can be spent only once:
        \begin{enumerate}
            \item Add $H(tx)$ to $D_{n_1, n_2}$. 
        \end{enumerate}
\end{enumerate} 
This is enough to prove that the transaction was included in the confirmed state. 

\begin{remark}
    Transaction proof can be included in the original state-proof circuit.
    In this case, a state prover can include as many transaction proofs as they desire.
    It (almost) does not influence the resulting verification costs and proof size.
\end{remark}

The transaction proof contains $\log(n_2 - n_1) + \log(k)$ hashes where $k$ is number of transactions in the block. 
Note that only the transaction's hash value will be written to Ethereum's storage.
All required information is available to the light client.

\input{chapters/generator/proof/introduction}
\input{chapters/generator/proof/optimizations}
\input{chapters/generator/proof/protocol}

\input{chapters/generator/circuit/introduction}
\input{chapters/generator/circuit/sha256}
\input{chapters/generator/circuit/poseidon}
\input{chapters/generator/circuit/merkle}
\input{chapters/generator/circuit/eddsa}
\input{chapters/generator/circuit/redshift}
\input{chapters/generator/circuit/correct_validator_set}
